Some Graphical Realizations of Two-Row Specht Modules of Iwahori-Hecke Algebras of the Symmetric Group

### 2019-07-28 tex/Drafts/Draft-1.tex
Bibliography hrefs

  \documentclass{amsart}   
  \usepackage{../RepStyle}

  % Colors links
  \hypersetup{
  colorlinks,
  citecolor=blue,
  linkcolor=black!30!magenta,
  urlcolor=blue}

@@

\section{Empirical Results}\label{Empirics Section}
In this section we aim both to support conjecture with data and to provide transition matrices wherever possible between our two graphical representaitons.
All data will be generated via tools available on \underline{\href{https://github.com/nataliesstewart/Hecke-Heuristics}{github}}.\footnote{The full URL to the repository is \underline{\href{https://github.com/nataliesstewart/Hecke-Heuristics}{https://github.com/nataliesstewart/Hecke-Heuristics}}.}

@@

\appendix
\section{Compatibility of Representations with the Relations}
In general, we define representations above for the free algebra on generators $\cbr{T_i}$.
Recall that we may give a presentation of $\SH$ having generators $T_i$ and relations
\begin{align}
  (T_i - q)(T_i + 1) &= 0 \label{quadratic}\\
  T_iT_{i+1}T_i &= T_{i+1}T_iT_{i+1} \label{braid1}\\ 
  T_iT_j &= T_jT_i \hspace{40pt} \abs{i - j} > 1. \label{braid2}
\end{align}
We call \eqref{quadratic} the \emph{quadratic relation} and \eqref{braid1}, \eqref{braid2} the \emph{braid relations}.
It is easily seen that a representation of $\SH$ is equivalent to a representation of the free algebra $k\langle T_i \rangle$ which acts as 0 on the relations (henceforth referred to as \emph{compatibility} with the relations).
We will prove in the following sections that $V$ and $W$ are compatible with the Hecke algebra relations.

>>>>

  \documentclass{amsart}   
  \usepackage{../RepStyle} 
  % Colors links
  \hypersetup{
  colorlinks,
  citecolor=blue,
  linkcolor=black!30!magenta,
  urlcolor=blue}

@@

\section{Empirical Results}\label{Empirics Section}
In this section we aim both to support conjecture with data and to provide transition matrices wherever possible between our two graphical representaitons.
All data will be generated via tools available on \href{https://github.com/nataliesstewart/Hecke-Heuristics}{github}.\footnote{The full URL to the repository is \href{https://github.com/nataliesstewart/Hecke-Heuristics}{https://github.com/nataliesstewart/Hecke-Heuristics}.}

@@

\newpage
\appendix
\section{Compatibility of Representations with the Relations}
In general, we define representations above for the free algebra on generators $\cbr{T_i}$.
Recall that we may give a presentation of $\SH$ having generators $T_i$ and relations
\begin{align}
  (T_i - q)(T_i + 1) &= 0 \label{quadratic}\\
  T_iT_{i+1}T_i &= T_{i+1}T_iT_{i+1} \label{braid1}\\ 
  T_iT_j &= T_jT_i \hspace{40pt} \abs{i - j} > 1. \label{braid2}
\end{align}
We call \eqref{quadratic} the \emph{quadratic relation} and \eqref{braid1}, \eqref{braid2} the \emph{braid relations}.
It is easily seen that a representation of $\SH$ is equivalent to a representation of the free algebra $k\langle T_i \rangle$ which acts as 0 on the relations (henceforth referred to as \emph{compatibility} with the relations).
We will prove in the following sections that $V$ and $W$ are compatible with the Hecke algebra relations.
